Financialisation of Commodity Markets

### 2024-12-04 docs/paper.qmd
Refactor
make_commodity_pool_tickers_dataframe() and cross correlations analysis

table_name <- "correlations - cross - periods"
columns_to_collapse_rows_for <- c("portfolios", "regime")
colnames <- c("portfolios", "regime", periods)
align <- make_series_of_repeated_chars(list(l = 1L, r = 5L))
longtable <- TRUE
bold_columns <- 1L:2L
coloured_columns <- 3L:6L

>>>>

table_name <- "correlations - cross - US - periods"
columns_to_collapse_rows_for <- c("portfolios", "regime")
colnames <- c("portfolios", "regime", periods)
align <- make_series_of_repeated_chars(list(l = 1L, r = 5L))
longtable <- TRUE
bold_columns <- 1L:2L
coloured_columns <- 3L:6L
